%-------------------------
% Resume in Latex
% Author : Jake
% % License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  urlcolor=MidnightBlue,  % nice subtle blue
  linkcolor=black,
  citecolor=black
}

\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

\begin{center}
    \textbf{\Huge \scshape James Widner} \\ \vspace{1pt}
    \small 678-977-9921 $|$ 
    \href{mailto:jameswidner2@gmail.com}{jameswidner2@gmail.com} $|$
    \href{https://github.com/pi128}{github.com/pi128} $|$
     \href{https://pi128.github.io/blog-of-james/portfolio.html}{Portfolio}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Kennesaw State University}{Marietta, GA}
      {B.S. in Computer Science,}{Aug. 2023 -- May 2026}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Software Engineering Intern}{Summer 2024}
  {\href{https://traxrfid.com/}{\textcolor{black}{Trax RFID}}}{Alpharetta, GA}
\resumeItemListStart
  \resumeItem{Contributed to an RFID tracking platform using \textbf{UHF RFID} to monitor car inventory across factory lots.}
  \resumeItem{Implemented front-end features and UI components, integrating with backend APIs to support real-time asset visibility.}
  \resumeItem{Collaborated in a fast-paced startup team, gaining experience in rapid prototyping and iteration.}
\resumeItemListEnd

\resumeSubheading
  {Software Engineering Intern}{Summer 2025}
  {\href{https://manwe-io.github.io/}{\textcolor{black}{Manwe (Cybersecurity Consulting Firm)}}}{Canton, GA}
\resumeItemListStart
  \resumeItem{Conducted basic penetration testing and stress testing on client systems to identify vulnerabilities and performance bottlenecks.}
  \resumeItem{Assisted with bug fixes, wrote unit tests, and contributed to improving code quality through reviews and daily standups.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------PROJECTS-----------

\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{Bulletin Generator} $|$ \emph{Python, SQLite, Docker, docx templating, JavaScript}}
  {Jun. 2025 -- Aug. 2025}
\resumeItemListStart
  \resumeItem{Automated weekly Anglican bulletins by dynamically populating \textbf{.docx templates} with lectionary readings, psalms, hymns, and prayers from the 1928 BCP.}
  \resumeItem{Built a \textbf{SQLite database} keyed to liturgical dates to fetch the appointed texts.}
  \resumeItem{Added template hot-swapping, enabling users to switch bulletin layouts or add custom sections without code changes.}
  \resumeItem{Packaged as a Slack bot with a setup wizard for deployment on a QNAP NAS server.}
\resumeItemListEnd

\resumeProjectHeading
  {\textbf{\href{https://cr8ova.com}{\textcolor{black}{Cr8ova — Music Creator Platform}}} $|$ \emph{React, Node.js, PostgreSQL, REST APIs}}
  {May 2025 -- Present}
\resumeItemListStart
  \resumeItem{Developed a platform for artists to share content, connect with other creators.}
  \resumeItem{Implemented authentication, content upload, and social features using \textbf{React} and \textbf{Node.js}.}
  \resumeItem{Built responsive UI and backend APIs supporting media streaming and community interaction.}
\resumeItemListEnd

\resumeSubHeadingListEnd

\section{Other Experience}
\resumeSubHeadingListStart

\resumeSubheading
  {Bike Shop Technician}{Mar. 2025 - Jul. 2025}
  {Cartersville Bike Shop}{Cartersville, GA}
\resumeItemListStart
  \resumeItem{Performed tune-ups, repairs, and full builds of customer bicycles, ensuring safety and quality.}
  \resumeItem{Delivered customer service and product recommendations, balancing technical expertise with client needs.}
\resumeItemListEnd

\resumeSubheading
  {Lifeguard}{2022 -- 2023}
  {Cherokee Aquatic Centre}{Canton, GA}
  
\resumeItemListStart
    \resumeItem{Monitored pool area to prevent accidents and ensure patron safety.}
    \resumeItem{Assisted with pool maintenance, including water pH testing and cleaning.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Go, Java, C#, Python, SQL, JavaScript} \\
     \textbf{Frameworks}{: WebAssembly (WASM), React, Node.js} \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, Visual Studio, Vim, IntelliJ, Android Studio} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, Flask, Express.js}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}